### 2018-09-13 manuscript.tex
Update manuscript.tex

\subsubsection{Conclusions}\label{conclusions}
Under the background that MC is not challenged in the West (e.g., against Jewish community), how  shall we frame FGC to be process by both communities from inside and outside?

\jd{I don't understand the North-South framing. Isn't MC not challenged everywhere? Shouldn't the framing be gender?}

@@

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would expect a majority under 15, no?} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (to update), and the actual numbers might in fact higher \cite{GaluKama15} (more?).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ for update) \jd{This claim is surprising, and the sources are not academic.}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.  The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).  Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}

There are at least three main theoretical perspectives \jd{WHAT: from outside the communities}
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important tool to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

\cf{\cite{Shel-Wand11}:  Mackie's social convention theory was supported in their findings \jd{Whose findings? I've lost track of this s.}; futher, they proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.

Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).  There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.  Although convention theory was well studied and showed a larger effect on FGC practices than other theories of modernization and feminism (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), the aforementioned theories did not necessarily excluded each other, especially between modern theory and feminist theory \cite{Hayf05}.

@@

Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))

>>>>

\subsubsection{Conclusions}\label{conclusions}

@@

It was estimated that more than 200 million women, of which 44 millions were girls under age 15, \jd{This ratio seems super-low. I would expect a majority under 15, no?}\cf{Most of the surveys sampled women of 15-49, girls under 15  were reported by their mothers. The ration of girls under 15 is minority} have undergone female genital cutting (FGC), mostly observed in Africa and the Middle East \cite{UNFPA14, UNIC16} (updated Sep 18).  The current progress of ending FGC is insufficient to keep up with the population growth, and girls and women undergoing FGC will rise significantly over the next 15 years if the trends continue \cite{UNIC16} (also see http://www.who.int/mediacentre/factsheets/fs241/en/ updated Sep, 18) \jd{This claim is surprising, and the sources are not academic.}\cf{UN is supposed to be reliable and often quoted by academic papers}.  FGC is also known as female genital mutilation and female circumcision; we use cutting instead because it \jd{What: implies a degree of self-awareness and} is considered less judgmental \cite{KhahBark09, JohnEsse10, Meye00, Shel01} (and is adapted by Tostan (http://www.tostan.org/)).

The commonly shared position for FGC is more about eradication than intervention \cite{Toub94, Mack96, UNIC16} (more cites); but the progress is hindered due to the complicated history of the very practice.  The meanings of FGC are competitively defined by various groups from local religious community to international governmental institutes, by linking the practice to religious identity in one end and to human rights on the other \cite{Boyl02, SchuLien13, WHO12} (more cites).  Interventions based on associating FGC with violations of human rights and health dangers also encountered challenges \cite{MuthSvan15}, for example, for overlooking a discrepant tolerance between FGC and male circumcision \cite{DarbSvob07, JohnEsse10}, the complexity of woman's autonomy \cite{Meye00}, and cultural perspectives of local history and identity, therefore was often defied by local communities, despite that the practice was often endorsed by national governments \cite{Boyl02, BoylMcMo02, BoylCarb10, Grue05, Koom14, PerrSeni13, Shel08, ShelWand13, Wade11} (update cites). \jd{I think we have two choices. Either we accept the WHO ``consensus'' that it's always bad, or start discussing types.}\cf{The main purpose of this study is not to discuss types or take a position. This paragraph is to briefly present fgc in context.}

There are at least three main theoretical perspectives from outside the FGC communities
shedding lights on the complexities of FGC \cite{Hayf05, Youn02}:  social convention theory \cite{Mack96, Mack00, Mack06, MackLeJe09, DuncWand11}, modernization theory\cite{BoylMcMo02, Youn02} (confirm, and update), and feminist theory/human rights perspective \cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02}, such as women's autonomy \cite{Meye00} and women's body and pleasure (\cite{Morr08} on Gayatri Spivak) (confirm and update.)  Convention theory posits FGC an important norm to control marriage fidelity and social prestige; this perspective views FGC as a social behaviour resulting from group practice, and it takes a ``critical mass" to initiate a change \cite{Mack00, MackLeJe09}.  When norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, Mack96, Mack06, MackLeJe09, ThomMadd92}; hence, intervention of FGC should target women's social networks, which are intergenerational, interdependent and interconnected across generations and genders \cite{Mack00, DuncWand11}.

Modernization theory proposes that traditional social relationships and values would be eroded by modernization (e.g., with the improvement of wealth and education and emphasis of individual rights) (see\cite{Moor13}) (and \cite{BoylMcMo02, Youn02}?).  There is a wide range of gender theories on FGC (see\cite{Anti13, Hodg11, Lewi95}) and woman's empowerment on making FGC decision are shared concerns:  for example, from social position \cite{VanMeek15}, autonomy \cite{Meye00}, gender equality and human rights \cite{Drol11}, to gender identity \cite{Youn04, Koom14, WintKoom09}.  Although convention theory was well studied and showed a larger effect on FGC practices than the others (e.g, \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}), these theories did not necessarily excluded each other, especially between modernization theory and feminist theory \cite{Hayf05}.

@@

Only women \jd{What does this mean: with daughters to be considered} for fgc were included in the main model (the daughter model) and the future-dughter model, while the future model included all the women in the samples; that resulted in xxx, xxx and xxx (or three more if sample sizes in individual models are different from the full models) respectively.
\jd{We need to know how DHS decided who to ask the question.}
\cf{Explain how we choose women}

@@

--Main interpretation --
--- conventional \cite{FreyJohn07, Hayf05, Mack96, ShelWand11} vs. modernization (cite{BoylMcMo02, Youn02}, education and wealth as index of modernization), vs. gender \cite{Dell04, FrieMahm13, Lewi04, Meye00, Njam04, YirgKass12, Youn02} (more and confirm).  
% women's empowerment appeared to be more important in explaining differences across communities\cite{ModrLiu13} (more).
% ``attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}
\cf{Mackie's social convention theory was supported in \cite{Shel-Wand11}; futher, \cite{Shel-Wand11} proposed that reasons for fgc practice go beyond the belief that it is advantageous for marriage prospects. FGC allows women to gain social capitals and access to networks.  Their findings also suggested that the main deterent to marriages was not men's refusal of non-fgc women, but hostility and discrimination from fgc women to non fgc women}.
--- community levels of impact and intervention
\cite{Drot11, Grue05, JoneEhir04} (both on cultural perspective, and maybe norm), 
\cite{ChegAske04}(community -based approach), \cite{BrowBeec13,PatrSing15}
--- attitudes vs. norm (beliefs) vs. intention (intended behaviors, planned behavior, controlled behavior) \cite{Ajze02, ThomMadd92}
\cite{TerrHogg96}:  subjective norm on attitude and planned behavior.  There were three main predictors of intentio:  attitude, norm and perceived behavioroal control.
\cite{EffeVogt15}:  Efferson proposed that cutting is not a social norm based on ``coordination."  The problem is that he and his colleages conclusion was based on a marraige market associating with cutting.  But it is likely that fgc is much less an action for marraige proposal but a social indentity to the group they indentify with.
\cite (The social construction of reality: a treatise in the sociology of knowledge Anchor Books, New York, NY (1966))
